Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-16 paper/conclusion.tex
Revise conclusion

Aside from adding expressiveness to the code contract language, future work is to formally verify every transformation step from the code contract to the final \ckml\ function that is compiled to the target binary. 
The HOL embedding of the code contract semantics we discussed here is the starting point.
The key steps are as follows:
\begin{compactitem}
  \item Automatically add state to the code contract to remove $\konst{pre}(-)$ and prove the initial and modified contracts are equivalent for all input streams
  \item Create a step based version of the modified code contract that does not use streams and prove it equivalent to the stream version.
  \item Create a pure HOL4 function, suitable to \ckml\, from the step version of the code contract and prove it equivalent.
\end{compactitem}
We have automated in HOL4 the transformation to remove $\konst{pre}(-)$ in the first step in what we call \emph{temporal squashing}.
We have additionally manually written proofs for every step for a set of example code contracts.
From the manual proofs, we have started work on proofs for the first two steps that are universal in that they reason over any input code contract.
The third step must be generated for each input contract, and the entire process still needs to be mechanized.
Other future work includes lifting the proof results to infinite streams.

>>>>

Aside from adding expressiveness to the code contract language, future work is to formally verify every transformation step from the code contract to the final \ckml\ function that is compiled to the target binary. 
The HOL4 embedding of the code contract semantics we discussed here is the starting point.
The key steps are as follows:
\begin{compactitem}
  \item Automatically add state to the code contract to remove $\konst{pre}(-)$ and prove the initial and modified contracts are equivalent for all input streams
  \item Create a step based version of the modified code contract that does not use streams and prove it equivalent to the stream version
  \item Create a pure HOL4 function, suitable to \ckml, from the step version of the code contract and prove it equivalent
\end{compactitem}
We have automated in HOL4 the transformation to remove $\konst{pre}(-)$ in the first step in what we call \emph{temporal squashing}.
We have additionally manually written proofs for every step for a set of example code contracts.
From the manual proofs, we have started work on proofs for the first two steps that are universal in that they reason over any input code contract.
The third step must be generated for each input contract, and the entire process still needs to be mechanized.
Other future work includes lifting the proof results to infinite streams.
